### 2024-11-23 paper/background.tex
Add explanation for structured control flow

% execution
Wasm execution is based on a stack machine.
An instruction consumes values from the stack as operands, performs an
operation, and pushes the resulting values onto the stack.
For example, the \texttt{testop} instruction exemplifies how this execution
model operates in practice.
\cref{fig:testop} illustrates the Wasm specification document for the
\texttt{testop} instruction.
It describes its semantics using two complementary forms: prose notation and
formal notation.
The prose notation is written in the upper part, and the formal notation is
written in the lower grey box.
In the prose notation, the instruction pops a value from the stack, performs a
test operation, and pushes the result back onto the stack.
In the formal notation, this is compactly expressed as a reduction rule
consisting of the left-hand side (LHS), right-hand side (RHS), and premises:
$(t.const ~ c_1) ~ t.testop$, $(i32.const ~ c)$, and $c = testop_t(c_1)$,
respectively.
The LHS indicates that the value at the top of the stack is $(t.const ~ c_1)$,
and the instruction to execute is $t.testop$.
The RHS shows that the value at the top of the stack is updated to $(i32.const
~ c)$, which occurs if the premise $c = testop_t(c_1)$ holds true.
% Additionally, the stack also stores structures related to the control flow
% along with the input and output values of the instructions: A \textit{frame}
% for function calls and a \textit{label} for branching.

>>>>

% Execution
Wasm execution is based on a stack machine.
An instruction consumes values from the stack as operands, performs an
operation, and pushes the resulting values onto the stack.
For example, the \texttt{testop} instruction exemplifies how this execution
model operates in practice.
\cref{fig:testop} illustrates the Wasm specification document for the
\texttt{testop} instruction.
It describes its semantics using two complementary forms: prose notation and
formal notation.
The prose notation is written in the upper part, and the formal notation is
written in the lower grey box.
In the prose notation, the instruction pops a value from the stack, performs a
test operation, and pushes the result back onto the stack.
In the formal notation, this is compactly expressed as a reduction rule
consisting of the left-hand side (LHS), right-hand side (RHS), and premises:
$(t.const ~ c_1) ~ t.testop$, $(i32.const ~ c)$, and $c = testop_t(c_1)$,
respectively.
The LHS indicates that the value at the top of the stack is $(t.const ~ c_1)$,
and the instruction to execute is $t.testop$.
The RHS shows that the value at the top of the stack is updated to $(i32.const
~ c)$, which occurs if the premise $c = testop_t(c_1)$ holds true.
% Additionally, the stack also stores structures related to the control flow
% along with the input and output values of the instructions: A \textit{frame}
% for function calls and a \textit{label} for branching.

% Structured Control Flow
Wasm supports control instructions for structured control flow, which
eliminates the need for arbitrary jumps, ensuring structured and predictable
execution.
Control instructions include \texttt{blocks}, \texttt{call}, \texttt{br}, and
\texttt{return}, which are explicitly delimited in the code.
Each control instruction is associated with \textit{contexts} that facilitate
structured execution and aid in handling nested or complex control flows.
For instance, the \texttt{block} instruction groups a sequence of instructions
and provides a scoped execution context with a \textit{label}, while the
\texttt{call} instruction executes body of a function with a \textit{frame}.
The \texttt{br} and \texttt{return} instructions jumps to the beginning or
the end of the block and the function, specified within the contexts, providing
targeted control transfers.
